Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-19 stp/paper_aaai/main.tex
Experiments section partially

\npr{Should I mention complex matches like 1:n and n:1 and iMap?}

@@

Future directions:
incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
incorporate schema and ontology constraints.

>>>>

@@

Future directions:
incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
incorporate schema and ontology constraints;
complex matches like 1:n and n:1 and iMap.
